---
title: "Document Including all My Homework Answers"
author: "22015"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Document Including all My Homework Answers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

All my homework answers about Statistical Computing class.

# HW0: "A-22015-2022-09-09"

## Example 1

#### Simple description: some exercises about R basic use.

```{r}
seq(1, 5, 0.5)
seq(length=9, from=1, to=5)
rep(1,5)
sequence(4:5)
gl(2, 6, label=c("Male", "Female"))
expand.grid(h=c(60,80), w=c(100, 300), sex=c("Male", "Female"))
qnorm(0.975)
matrix(1:6, 2, 3, byrow=TRUE)
ts(1:47, frequency = 12, start = c(1959, 2))
```

## Example 2

#### Simple description: try to draw pictures.

```{r echo=FALSE}
x = rnorm(10)
y = rnorm(10)
plot(x, y, xlab="Ten random values", ylab="Ten other values",
     xlim=c(-2, 2), ylim=c(-2, 2), pch=22, col="red",
     bg="yellow", bty="l", tcl=0.4,
     main="How to customize a plot with R", las=1, cex=1.5)
```
```{r}
library(lattice)
n <- seq(5, 45, 5)
x <- rnorm(sum(n))
y <- factor(rep(n, n), labels=paste("n =", n))
densityplot(~ x | y,
            panel = function(x, ...) {
                panel.densityplot(x, col="DarkOliveGreen", ...)
                panel.mathdensity(dmath=dnorm,
                                  args=list(mean=mean(x), sd=sd(x)),
                                  col="darkblue")
})
```

## Example 3

#### Simple description: how to write a program by myself.

```{r}
ricker <- function(nzero, r, K=1, time=100, from=0, to=time) {
    N <- numeric(time+1)
    N[1] <- nzero
    for (i in 1:time) N[i+1] <- N[i]*exp(r*(1 - N[i]/K))
    Time <- 0:time
    plot(Time, N, type="l", xlim=c(from, to))
}
ricker(0.1, 1); title("r = 1")
```

## Example 4

#### Simple description: An convenient function -- use  xtable to get the table in latex form.

```{r}
xtable::xtable(head(iris))
```

## Example 5

#### Simple description: an easy exercise about how to import data and write formula in latex forms.
  
```{r}
data = read.table("../data/Bank_loan.txt",head=TRUE,na.strings = c("NA"))
past.customers = subset(data,default != "NA")
pie(c(sum(past.customers$default == 1),sum(past.customers$default == 0)),c(1,0))
for (i in 1:4){
a = nrow(past.customers[past.customers$default ==0 & past.customers$edu == i,])/nrow(past.customers[past.customers$edu==i,])
b = nrow(past.customers[past.customers$default ==1 & past.customers$edu == i,])/nrow(past.customers[past.customers$edu==i,])
if (i == 1){
  b_0 = b
  a_0 = a
  next
}
a_0 = c(a_0,a)
b_0 = c(b_0,b)
}
probability_on_condition = data.frame(c(1:4),a_0,b_0)
```


