---
title: "Introduction to StatComp22015"
author: "22015"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp22015}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp22015__ is a simple R package developed to compare the performance of R and R++ (implemented through the R package _Rcpp_) for the 'Statistical Computing' course. Two functions are considered, namely, _gibbs_ (generate random nubers using Gibbs sampler) and _vacc_ (predicting the response using three variables: age, gender, and ily). For each function, both R and Rcpp versions are produced. Namely _gibbsR_ and  _vaccR_ for R and 'gibbC' and _vaccC_ for C++.

The R package 'microbenchmark' can be used to benchmark the above R and C++ functions.


```{r,eval=TRUE}
library(StatComp22015)
library(microbenchmark)
```

The above results show an evident computational speed gain of C++ against R.


## Benchmarking _gibbsR_ and _gibbsC_

The source R code for _vaccR_ is as follows:
```{r,eval=FALSE}
gibbsR <- function(N, thin) {
  mat <- matrix(nrow = N, ncol = 2)
  x <- y <- 0
  for (i in 1:N) {
    for (j in 1:thin) {
      x <- rgamma(1, 3, y * y + 4)
      y <- rnorm(1, 1 / (x + 1), 1 / sqrt(2 * (x + 1)))
    }
    mat[i, ] <- c(x, y)
  }
  mat
}
```

The above R code involves two loops, which could be very slow even for R-3.01 or any higher version. The corresponding C++ code is as follows.

```{r,eval=FALSE}
NumericMatrix gibbsC(int N, int thin) {
  NumericMatrix mat(N, 2);
  double x = 0, y = 0;
  for(int i = 0; i < N; i++) {
    for(int j = 0; j < thin; j++) {
      x = rgamma(1, 3, 1 / (y * y + 4))[0];
      y = rnorm(1, 1 / (x + 1), 1 / sqrt(2 * (x + 1)))[0];
    }
    mat(i, 0) = x;
    mat(i, 1) = y;
  }
  return(mat);
}
```

The R code for benchmarking _gibbsR_ and _gibbsC_ is as follows.

```{r,eval=TRUE}
tm2 <- microbenchmark(
  vR = gibbsR(1e4, 10),
  vC = gibbsC(1e4, 10)
)
knitr::kable(summary(tm2)[,c(1,3,5,6)])
```

The results again show an evident computational speed gain of C++ against R.

